\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue, roman]{casual}
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Yudong}
\familyname{Xiao}
\title{Curriculum Vitae}
\mobile{+86 18618327879}
\email{xiaoyudong0512@gmail.com}
%%\address{Room 724, Central Main Building, Tsinghua University}{100084, Beijing}{China}
%% \quote{``Do what you fear, and the death of fear is certain.''\\-- Anthony Robbins}

%\phone{(312) 413-8265}                      % optional, remove the line if not wanted
%\fax{312 996 1491}                          % optional, remove the line if not wanted
%\photo[64pt]{avatar.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%% \renewcommand*{\sectionfont}{\LARGE\sffamily\monospace\slshape}
%% \renewcommand*\addressfont{\fontfamily{pzc}\selectfont}
%% \renewcommand*\sectionfont{\fontfamily{pzc}\fontsize{20}{24}\selectfont}

\begin{document}
\maketitle

\section{Education}
\cventry{2012--Present}{MS in Computer Science \& Technology, Supervisor: Qionghai Dai}{Computer School, Tsinghua University}{expected 2015}{}{}
\cventry{2008--2012}{BA in Computer Science \& Technology}{Computer School, Beijing University of Post \& Telecommunications}{}{}{}

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}

\section{Internship}
\cventry{2014.04--09}{Microsoft Research Asia, Software Analytic Group}{Data Mining Intern}{}{}{With Microsoft's distributed computing platform COSMOS, participated in development of Time series-based Abnormally Detection System on Improved Emerging  Pattern Mining, and optimized to stable version.}
\cventry{2012.04--08}{Huawei the Noah’s Ark Lab}{Data Mining Intern}{}{}{Hadoop platform, realizing the Apriori correlation algorithm for telecom device failure analysis on the huge historical fault log.}
\cventry{2011.09--12}{Beijing RenRen Inc}{iOS DEV Intern}{}{}{Participated in the development of two online versions of RenRen iOS client’s location and album modules, ensuring that no major bugs.}

\section{Community}
\cventry{Blog}{\url{imsheridan.com}}{My blog (Chinese)}{}{}{}
\cventry{GitHub}{\url{github.com/imsheridan}}{}{}{}{}

\section{Project Experience}
%% \subsection{Research Projects}

\cventry{2014--present}
{Emerging Pattern Mining}
{CSharp, COSMOS}
{Startup Project}{}
{
Emerging Pattern Mining is a startup project, aimed at finding out the real reason of significant change in multi-dimensional time series-based data.\\
I have been working as a full-time intern in Sofware Analytic Group of Microsoft Research Asia, and responsible for designing and implementing a distributed abnormally detection system on Microsoft's distributed computing platform COSMOS, including frequent itemset mining by FP-Tree, change detection by GLR, entropy-based redundant pruning and result ranking.
}

\vspace*{0.2\baselineskip}
\cventry{2013--2014}
{DeLogo}
{Matlab}
{Research Project}{}
{Working with Liheng Bian, Prof. Lei Zhang, Prof. Jinli Suo and Prof. Qionghai Dai. \\
DeLogo is a video logo removal system that can automatically and perfectly remove and repair the logo area. Mathematically, we treat inpainting as a global optimization with a linear system incorporating both the temporal video consistency and the priors of the inpainting regions. Further, we propose a numerical solution to above optimization based on Augmented Lagrangian
Method. \\
I was the major contributor of this project and the paper has been accepted in ICIP '14.
}

\vspace*{0.2\baselineskip}
\cventry{2014}
{Fast Ghost Imaging}
{C++, Matlab}
{Research Project}{}
{Working with Liheng Bian, Prof. Lei Zhang, Prof. Jinli Suo and Prof. Qionghai Dai. \\
Computational ghost imaging needs to acquire a large number of correlated measurements between reference patterns and the scene for reconstruction.\\
This project proposes a self-synchronization scheme that can eliminate this difficulty by introducing a high precision synchronization technique and corresponding algorithm. We physically implement the proposed scheme using a 20kHz spatial light modulator to generate random binary patterns together with a 100 times faster photodiode for high speed ghost imaging, and the acquisition frequency is around 14 times faster than that of state-of-the-arts. \\
I was the major contributor of this project and the paper has been submitted to Optics Letter (OL, IF 3.385).
}

\section{Research}

\cventry{2014}
{\textbf{Yudong Xiao}\textnormal{, Jinli Suo, Liheng Bian, Lei Zhang, and Qionghai Dai}}
{"Automatic Inpainting of Linearly Related Video Frames"}{IEEE International Conference on Image Processing, 2014}
{}{}{}

\cventry{2014}
{\textnormal{Jinli Suo, }\textbf{Yudong Xiao}\textnormal{, Liheng Bian, Lei Zhang, and Qionghai Dai}}
{"Self synchronizing scheme for high speed ghost imaging"}
{submitted to Optics Letter (OL, IF 3.385)}
{}{}{}
\cventry{2014}
{\textnormal{Tao Yue, Jinli Suo, }\textbf{Yudong Xiao}\textnormal{, Lei Zhang, and Qionghai Dai}}
{"Image Quality Enhancement Using Original Lens via Optical Computing"}
{submitted to  Optics Express ((OE, IF 3.546)}
{}{}{}
\cventry{2013}
{\textnormal{Yuqing Lu, Lei Zhang, }\textbf{Yudong Xiao}\textnormal{, and Yangguang Li}}
{"Simultaneously detecting fake reviews and review spammers using factor graph model"}
{ACM Web Science 2013}
{}{}{}

\section{Skills}
\cventry{Languages}{C/C++ = Matlab = Objective-C > JAVA = Python}{}{}{}{}
\cventry{Major}{Data Mining, Computer Vision}{Solid basic knowledge in data mining, machine learning and computer vision related}{}{}{}
\cventry{English}{CET-6 551}{skilled at reading \& translation of domain materials.}{}{}{}

% \closesection{}                   % needed to renewcommands
% \renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%cvlistdoubleitem[\Neutral]{Item 3}{}

\end{document}
